
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
10pt, % Main document font size
a4paper, % Paper type, use 'letterpaper' for US Letter paper
oneside, % One page layout (no page indentation)
%twoside, % Two page layout (page indentation for binding and different headers)
headinclude,footinclude, % Extra spacing for the header and footer
BCOR5mm, % Binding correction
]{scrartcl}

\input{structure.tex} % Include the structure.tex file which specified the document structure and layout

\hyphenation{Fortran hy-phen-ation} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

% Switch font to helvectica (enclose in curly braces for local scope)
\newcommand*{\helvetica}{\fontfamily{phv}\selectfont}

%----------------------------------------------------------------------------------------
%	TITLE AND AUTHOR(S)
%----------------------------------------------------------------------------------------

\title{\normalfont\spacedallcaps{Daniel Ritchie}} % The article title

\author{\spacedallcaps{Publication List}} % The article author(s) - author affiliations need to be specified in the AUTHOR AFFILIATIONS block

\date{} % An optional date to appear under the author(s)



\begin{document}

%----------------------------------------------------------------------------------------
%	HEADERS
%----------------------------------------------------------------------------------------

\pagestyle{scrheadings}
\clearscrheadings
\newcommand{\headertext}{\spacedlowsmallcaps{\color{black} Daniel Ritchie \color{halfgray} Publication List}}
\ohead{\headertext}
\cfoot[\pagemark]{\pagemark}


\maketitle

\section*{REFEREED PUBLICATIONS}
\textbf{Controlling Procedural Modeling Programs with Stochastically-Ordered Sequential Monte Carlo}. 
Daniel Ritchie, Ben Mildenhall, Noah D. Goodman, and Pat Hanrahan. 
In \emph{The Proceedings of SIGGRAPH 2015}.
\\ \\
\textbf{Generating Design Suggestions under Tight Constraints with Gradient-based Probabilistic Programming}. 
Daniel Ritchie, Sharon Lin, Noah D. Goodman, and Pat Hanrahan. 
In \emph{The Proceedings of Eurographics 2015}. \textbf{Best Paper Honorable Mention}
\\ \\
\textbf{Quicksand: A Lightweight Embedding of Probabilistic Programming for Procedural Modeling and Design}. 
Daniel Ritchie. 
In \emph{The 3rd NIPS Workshop on Probabilistic Programming, 2014}.
\\ \\
\textbf{First-class Runtime Generation of High-performance Types using Exotypes}. 
Zach Devito, Daniel Ritchie, Matthew Fisher, Alex Aiken, and Pat Hanrahan. 
In \emph{The Proceedings of PLDI 2014}.
\\ \\
\textbf{Probabilistic Color-by-Numbers: Suggesting Pattern Colorizations Using Factor Graphs}. 
Sharon Lin, Daniel Ritchie, Matthew Fisher, and Pat Hanrahan. 
In \emph{The Proceedings of SIGGRAPH 2013}.
\\ \\
\textbf{Example-based Synthesis of 3D Object Arrangements}. 
Matthew Fisher, Daniel Ritchie, Manolis Savva, Thomas Funkhouser, and Pat Hanrahan. 
In \emph{The Proceedings of SIGGRAPH Asia 2012}.
\\ \\
\textbf{d.tour: Style-based Exploration of Design Example Galleries}. 
Daniel Ritchie, Ankita Arvind Kejriwal, and Scott R. Klemmer. 
In \emph{The Proceedings of UIST 2011}.
\\ \\
\textbf{Dynamic Local Remeshing for Elastoplastic Simulation}. 
Martin Wicke, Daniel Ritchie, Bryan M. Klingner, Sebastian Burke, Jonathan R. Shewchuk, and James F. O'Brien. 
In \emph{The Proceedings of SIGGRAPH 2010}.
\\ \\
\textbf{Interactive Simulation of Surgical Needle Insertion and Steering}. 
Nuttapong Chentanez, Ron Alterovitz, Daniel Ritchie, Lita Cho, Kris K. Hauser, Ken Goldberg, Jonathan R. Shewchuk, and James F. O'Brien. 
In \emph{The Proceedings of SIGGRAPH 2009}. 

\section*{TECHNICAL REPORTS}
\textbf{C3: Lightweight Incrementalized MCMC for Probabilistic Programs using Continuations and Callsite Caching}. 
Daniel Ritchie, Andreas Stuhlm\"uller, Noah D. Goodman. 
\emph{arXiv:1509.02151}, 2015.

\section*{BOOK CHAPTERS}
\textbf{Probabilistic Programming for Procedural Modeling and Design}. Daniel Ritchie, Pat Hanrahan, Noah D. Goodman. In Vikash Mansinghka and Daniel Roy (Eds.), \emph{Probabilistic Programming} (in preparation).

\end{document}


